---
title: "Introduction to fcmfd"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to fcmfd}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(fcmfd)

set.seed(123)
```

# Introduction

The **fcmfd** package implements fuzzy clustering
for ordinal Likert-type data using triangular
fuzzy numbers (TFNs).

# Example Dataset

```{r}
data(sim_likert7)

head(sim_likert7)
```

# Running the Clustering Algorithm

```{r}
result <- fcmTFN(
  data = sim_likert7,
  option = "B",
  k_values = 2:6
)

summary(result)
```

# Cluster Assignment

```{r}
clusters <- cluster_assignment(result)

table(clusters)
```

# Prototype Interpretation

```{r}
prototype_matrix(result)
```

# Xie-Beni Index Visualization

```{r}
plot_xb(result)
```

# Conclusion

This vignette demonstrated the basic workflow
for fuzzy clustering of Likert-type data
using the **fcmfd** package.
